Supporting Information for "Geometric models overestimate lake depth due to imperfect slope measurement"

### 2020-07-28 manuscript/si_template_2019.tex
prep for submission

\noindent\textbf{Contents of this file}
%%%Remove or add items as needed%%%
\begin{enumerate}
\item \textbf{Figure S1:} Map of study lakes

\item \textbf{Figure S2:} Hypsography classification by state

\item \textbf{Figure S3:} Comparison among lake shape and reservoir classes for true and proxy geometry measures

\item \textbf{Figure S4:} Importance plot for random forest variables showing increase in mean square error

\item \textbf{Figure S5:} Comparison between characteristics of lakes with bathymetry data against lakes with depth from other sources

\item \textbf{Figure S6:} Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status

\item \textbf{Figure S7:} Comparison between reported depth and depth extracted from bathymetry surfaces

%if Tables are larger than 1 page, upload as separate excel file
\end{enumerate}

@@

@@

>>>>

\noindent\textbf{Contents of this file}
%%%Remove or add items as needed%%%
\begin{enumerate}

\item \textbf{Figure S1:} Diagram showing expectations regarding depth prediction bias

\item \textbf{Figure S2:} Map of study lakes

\item \textbf{Figure S3:} Hypsography classification by state

\item \textbf{Figure S4:} Lake geometry comparison among shape and reservoir classes

\item \textbf{Figure S5:} Importance plot for random forest variables

\item \textbf{Figure S6:} Characteristics of lakes with bathymetry versus non-bathymetry lakes

\item \textbf{Figure S7:} Lake characteristics comparison among shape and reservoir classes

\item \textbf{Figure S8:} Comparison between reported depth and bathymetry depth

%if Tables are larger than 1 page, upload as separate excel file
\end{enumerate}
\vspace{1em}

@@

\begin{figure}
      \begin{center}
        \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/lake_shape}
      \end{center}
      \caption{Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right). Dashed lines represent extrapolated nearshore land slope while solid lines represent the lake bottom.}\label{fig2}
    \end{figure}

@@

\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States from \citeA{stachelek2020}). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{table1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
  \hline
  Variable & Median & Q25 & Q75 & n\\
  \hline
  Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4850 (17700)\\
  \textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4850 (17700)\\
  \textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4850 (17700)\\
  \textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4850 (17700)\\
  \textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4850 (17700)\\
  \textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4850 (17700)\\
  \textbf{Watershed-lake ratio} & 7.8 (10) & 3.9 (4.4) & 17 (28) & 4850 (17700)\\
  Distance to deepest point (m) & 180 (-) & 110 (-) & 290 (-) & 4850 (-)\\
  Distance to lake center (m) & 240 (-) & 160 (-) & 380 (-) & 4850 (-)\\
  In-lake slope (m/m) & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4850 (-)\\
  Nearshore land slope (m/m) & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4850 (-)\\
  \hline
  \end{tabular}
\end{table}
